---
title: "DEU no aggregation specificity"
author: "Sergio Manzano"
date: "2024-06-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Script preparation, echo=FALSE, warning=FALSE, message=FALSE}

# Install packages

#if (!require("BiocManager", quietly = TRUE))
    #install.packages("BiocManager")
#BiocManager::install("DEXSeq")



# Set the working directory
setwd("C:/Users/smanz/OneDrive/Escritorio/TFM/Results/Exon_COUNTS_noaggegation_specificity")



# Load the needed libraries
library(DEXSeq)


# Workflow: https://www.bioconductor.org/packages/devel/bioc/vignettes/DEXSeq/inst/doc/DEXSeq.html#6_Visualization

```


* # Patient 53


```{r DEXSeq Results}

#?DEXSeqResults

DexSetResults <- readRDS("DEXSeqResults.patient53_control.rds")
head(DexSetResults)
head(rownames(DexSetResults))

# Calculating proportions
table(DexSetResults$padj<0.05)
table(tapply(DexSetResults$padj < 0.05, DexSetResults$groupID, any)) # Number of genes that are affected: 


```

### Order of the genes: BRCA1, PTEN, TP53, MLH1, ATM, MSH6, CHEK2, RAD51D, PALB2, RAD51C, BARD1, CDH1, BRCA2, BRIP1, MSH2

* Genes of interest

```{r}

genes <- c("ENSG00000012048", "ENSG00000171862", "ENSG00000141510", "ENSG00000076242", "ENSG00000149311", "ENSG00000116062", "ENSG00000183765", "ENSG00000185379", "ENSG00000083093", "ENSG00000108384", "ENSG00000138376", "ENSG00000039068", "ENSG00000139618", "ENSG00000136492", "ENSG00000095002")


```

### Ploted thing (Because the default FDR value is set to 0.1)

```{r}

subset(DexSetResults, DexSetResults$groupID=="ENSG00000149311" & DexSetResults$padj < 0.1)

```
### Changing the FDR to 0.05 the plotted genes are the ones that have the p.adj < 0.05

```{r}

subset(DexSetResults, DexSetResults$groupID=="ENSG00000149311" & DexSetResults$padj < 0.05)

```

* Plots

```{r splicing}

# As explained in Section 1, DEXSeq is designed to find changes in relative exon usage, i.e., changes in the expression of individual exons that are not simply the consequence of overall up- or down-regulation of the gene. To visualize such changes, it is sometimes advantageous to remove overall changes in expression from the plots. Use the option splicing=TRUE for this purpose.

for (gene in genes){
  plotDEXSeq(DexSetResults, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}


output_dir <- "P53"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DexSetResults, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


For further explanations see Data/Results/RNAsplice/RNAsplice_DEU

## Read all the files

```{r}

DEXSEQ_list <- list()

patients_number <- c(54:99)
for (number in patients_number){
  DEXSeqResults.patient <- sprintf("DEXSeqResults.patient%d_control.rds", number)
  DEXSeqResults <- readRDS(DEXSeqResults.patient)
  DEXSEQ_list[[paste0("patient", number)]] <- DEXSeqResults
}

```



* # Patient 54

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient54, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P54"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient54, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}


```


* # Patient 55

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient55, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P55"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient55, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```

* # Patient 56

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient56, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P56"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient56, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 57

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient57, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P57"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient57, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 58

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient58, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P58"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient58, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```

* # Patient 59

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient59, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P59"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient59, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```

* # Patient 60

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient60, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P60"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient60, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 61

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient61, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P61"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient61, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```

* # Patient 62

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient62, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P62"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient62, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```

* # Patient 63

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient63, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P63"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient63, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```

* # Patient 64

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient64, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P64"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient64, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```

* # Patient 65

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient65, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P65"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient65, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 66

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient66, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P66"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient66, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 67

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient67, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P67"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient67, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 68

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient68, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P68"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient68, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 69

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient69, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P69"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient69, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 70

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient70, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P70"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient70, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 71

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient71, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P71"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient71, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 72

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient72, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P72"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient72, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 73

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient73, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P73"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient73, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 74

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient74, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P74"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient74, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 75

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient75, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P75"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient75, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 76

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient76, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P76"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient76, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 77

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient77, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P77"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient77, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 78

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient78, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P78"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient78, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 79

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient79, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P79"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient79, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 80

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient80, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P80"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient80, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```

* # Patient 81

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient81, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P81"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient81, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 82

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient82, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P82"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient82, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 83

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient83, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P83"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient83, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 84

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient84, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P84"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient84, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 85

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient85, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P85"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient85, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 86

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient86, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P86"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient86, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 87

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient87, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P87"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient87, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 88

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient88, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P88"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient88, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 89

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient89, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P89"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient89, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 90

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient90, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P90"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient90, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 91

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient91, gene, FDR = 0.05, expression=FALSE, splicing=TRUE, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P91"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient91, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 92

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient92, gene, FDR = 0.05, expression=FALSE, splicing=TRUE, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P92"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient92, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 93

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient93, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P93"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient93, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 94

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient94, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P94"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient94, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 95

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient95, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P95"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient95, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 96

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient96, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P96"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient96, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 97

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient97, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P97"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient97, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 98

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient98, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P98"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient98, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


* # Patient 99

```{r}

for (gene in genes){
  plotDEXSeq(DEXSEQ_list$patient99, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2 )
}

output_dir <- "P99"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}

for (gene in genes) {
  output_file <- file.path(output_dir, paste0(gene, ".png"))
  png(filename=output_file, width=800, height=600)
  plotDEXSeq(DEXSEQ_list$patient99, gene, expression=FALSE, splicing=TRUE, FDR = 0.05, legend=TRUE, cex.axis=1.2, cex=1.3, lwd=2)
  dev.off()
}

```


# Extract the exon positions of the DEU of the genes that have a local event

* ## Patient 76

```{r}

DexSeqResults76 <- readRDS("DEXSeqResults.patient76_control.rds")


subset(DexSeqResults76, DexSeqResults76$groupID=="ENSG00000141510" & DexSeqResults76$padj < 0.05)

subset(DexSeqResults76, DexSeqResults76$groupID=="ENSG00000149311" & DexSeqResults76$padj < 0.05)


```


* ## Patient 77

```{r}

DexSeqResults77 <- readRDS("DEXSeqResults.patient77_control.rds")


subset(DexSeqResults77, DexSeqResults77$groupID=="ENSG00000076242" & DexSeqResults77$padj < 0.05)

subset(DexSeqResults77, DexSeqResults77$groupID=="ENSG00000171862" & DexSeqResults77$padj < 0.05)


```


* ## Patient 79

```{r}

DexSeqResults79 <- readRDS("DEXSeqResults.patient79_control.rds")


subset(DexSeqResults79, DexSeqResults79$groupID=="ENSG00000076242" & DexSeqResults79$padj < 0.05)

subset(DexSeqResults79, DexSeqResults79$groupID=="ENSG00000083093" & DexSeqResults79$padj < 0.05)


```

* ## Patient 83

```{r}

DexSeqResults83 <- readRDS("DEXSeqResults.patient83_control.rds")


subset(DexSeqResults83, DexSeqResults83$groupID=="ENSG00000141510" & DexSeqResults83$padj < 0.05)



```

* ## Patient 84

```{r}

DexSeqResults84 <- readRDS("DEXSeqResults.patient84_control.rds")


subset(DexSeqResults84, DexSeqResults84$groupID=="ENSG00000141510" & DexSeqResults84$padj < 0.05)



```

* ## Patient 85

```{r}

DexSeqResults85 <- readRDS("DEXSeqResults.patient85_control.rds")


subset(DexSeqResults85, DexSeqResults85$groupID=="ENSG00000076242" & DexSeqResults85$padj < 0.05)

subset(DexSeqResults85, DexSeqResults85$groupID=="ENSG00000149311" & DexSeqResults85$padj < 0.05)



```


* ## Patient 91

```{r}

DexSeqResults91 <- readRDS("DEXSeqResults.patient91_control.rds")


subset(DexSeqResults91, DexSeqResults91$groupID=="ENSG00000149311" & DexSeqResults91$padj < 0.05)



```

# Session info

```{r}

sessionInfo()

```