---
title: "Table Local Events"
author: "Sergio Manzano"
date: "2024-06-04"
output:
  BiocStyle::html_document:
    theme: spacelab
    number_sections: true
    toc_float: true
    toc_depth: 3
---

```{r,, echo=FALSE, eval=FALSE, message=FALSE}

# NOTA: The R script named Table_of_LocalEvents.R does the same than this, but it is for running on the cluster (it is not in the github, only in the local computer).


```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Set the working directory

```{r, warning=FALSE, message=FALSE}

setwd("C:/Users/smanz/OneDrive/Escritorio/TFM/Results/Exon_COUNTS_noaggegation_specificity/Local_Events")

library(dplyr)
library(BiocStyle)

```

# **1. Inspect the data**

## Read the files

```{r}

file_list <- list.files("C:/Users/smanz/OneDrive/Escritorio/TFM/Results/Exon_COUNTS_noaggegation_specificity/Local_Events/LE_data")

for(i in 1:length(file_list)){
  file <- paste0("C:/Users/smanz/OneDrive/Escritorio/TFM/Results/Exon_COUNTS_noaggegation_specificity/Local_Events/LE_data/", file_list[i])
  LocalEvents <- read.csv(file, header = TRUE, sep = "\t", row.names = NULL) # If I read with \t I can see the headers, if I read with ";" I can split the parts
  assign(paste0("LocalEvents_", 53 + i - 1), LocalEvents)
}

```

## See the p-values distribution

```{r}

file_list <- list.files("C:/Users/smanz/OneDrive/Escritorio/TFM/Results/Exon_COUNTS_noaggegation_specificity/Local_Events/LE_data")

for (i in 1:length(file_list)) {
  file <- paste0("C:/Users/smanz/OneDrive/Escritorio/TFM/Results/Exon_COUNTS_noaggegation_specificity/Local_Events/LE_data/", file_list[i])
  LocalEvents <- read.csv(file, header = TRUE, sep = "\t", row.names = NULL)
  assign(paste0("LocalEvents_", 53 + i - 1), LocalEvents)
  
  p_val_column_name <- paste0("local_patient", 53 + i - 1, ".local_control_p.val")
  
  hist(get(paste0("LocalEvents_", 53 + i - 1))[, p_val_column_name], main = paste("Histograma for LocalEvents_", 53 + i - 1))
}

```

# **2. Filter the data**

## Select only the genes that have a p-value less than 0.05 and save them in a file separated by ";"

```{r, eval=FALSE}

file_list <- list.files("C:/Users/smanz/OneDrive/Escritorio/TFM/Results/Exon_COUNTS_noaggegation_specificity/Local_Events/LE_data")


for (i in 1:length(file_list)) {
  file <- paste0("C:/Users/smanz/OneDrive/Escritorio/TFM/Results/Exon_COUNTS_noaggegation_specificity/Local_Events/LE_data/", file_list[i])
  LocalEvents <- read.csv(file, header = TRUE, sep = "\t", row.names = NULL)
  assign(paste0("LocalEvents_", 53 + i - 1), LocalEvents)
  
  col_name <- paste0("local_patient", 53 + i - 1, ".local_control_p.val")
  filtered_events <- subset(LocalEvents, get(col_name) < 0.05)
  
  write.csv2(filtered_events, file = paste0("Filtered_Events/Filtered_Events_Patient_", 53 + i - 1, ".csv"), row.names = FALSE)
}


```

# **3. Work with the filtered data**

## *Load the data*

## Create the needed coumns for the final data frame (different patients) using filtered files

```{r}

filtered_list <- list.files("C:/Users/smanz/OneDrive/Escritorio/TFM/Results/Exon_COUNTS_noaggegation_specificity/Local_Events/Filtered_Events/")

for(i in 1:length(filtered_list)) {
  file <- paste0("C:/Users/smanz/OneDrive/Escritorio/TFM/Results/Exon_COUNTS_noaggegation_specificity/Local_Events/Filtered_Events/", filtered_list[i])
  LocalEvents <- read.csv2(file, header = TRUE, sep = ";", row.names = NULL) 
  
  colnames(LocalEvents) <- c("gene_name", "dPSI", "p.value")  

  assign(paste0("Local_Event_P", 53 + i - 1), LocalEvents)


}

```


## **Create de final data frame (without duplicates) and all genes**

```{r}

for (i in 1:length(filtered_list)) {
  file <- paste0("C:/Users/smanz/OneDrive/Escritorio/TFM/Results/Exon_COUNTS_noaggegation_specificity/Local_Events/Filtered_Events/", filtered_list[i])
  LocalEvents <- read.csv2(file, header = TRUE, sep = ";", row.names = NULL)
  
  colnames(LocalEvents) <- c("gene_name", "dPSI", "p.value")
  
  # Split gene_name by ":"
  gene_name_split <- strsplit(as.character(LocalEvents$gene_name), ":")
  genelocalevent <- sapply(gene_name_split, `[`, 1)
  
  # Split the results by ";"
  split_vector <- strsplit(genelocalevent, ";")
  gene_name <- sapply(split_vector, `[`, 1)
  local_event <- sapply(split_vector, `[`, 2)
  
  # Create the new data frame
  LocalEvents <- data.frame(gene_name = gene_name, local_event = local_event, dPSI = LocalEvents$dPSI, p.value = LocalEvents$p.value)
  LocalEvents_distinct <- distinct(LocalEvents)
  
  # Assign the new data frame to a variable with a dynamic name
  assign(paste0("Final_DF_P", 53 + i - 1), LocalEvents_distinct)
}


```


## Create the pattern to select the *interest genes*

```{r}

genes <- c("ENSG00000012048", "ENSG00000171862", "ENSG00000141510", "ENSG00000076242", "ENSG00000149311", "ENSG00000116062", "ENSG00000183765", "ENSG00000185379", "ENSG00000083093", "ENSG00000108384", "ENSG00000138376", "ENSG00000039068", "ENSG00000139618", "ENSG00000136492", "ENSG00000095002")
pattern <- paste(genes, collapse = "|")

```

## **Create de final data frame (without duplicates) with the selected genes**

* *First, without splitting the parts, in order to see the affected positions*

See the picture of the following link to understand the positions of the AS event: https://github.com/comprna/SUPPA?tab=readme-ov-file#psi-per-local-event

```{r}

for (i in 1:length(filtered_list)) {
  file <- paste0("C:/Users/smanz/OneDrive/Escritorio/TFM/Results/Exon_COUNTS_noaggegation_specificity/Local_Events/Filtered_Events/", filtered_list[i])
  LocalEvents <- read.csv2(file, header = TRUE, sep = ";", row.names = NULL)
  
  colnames(LocalEvents) <- c("gene_name", "dPSI", "p.value")
  
  # Create the new data frame
  LocalEvents <- data.frame(gene_name = LocalEvents$gene_name, dPSI = LocalEvents$dPSI, p.value = LocalEvents$p.value)
  
  # Filter genes matching the pattern
  pattern_matched <- grep(pattern, LocalEvents$gene_name)
  LocalEvents_filtered <- LocalEvents[pattern_matched, ]
  
  # Remove duplicates
  LocalEvents_distinct <- distinct(LocalEvents_filtered)
  
  # Create a dynamic name for the object
  object_name <- paste0("PositionGenes_DF_P", 53 + i - 1)
  
  # Assign the final dataframe to an object with a dynamic name
  assign(object_name, LocalEvents_distinct)
}

```


* *Second, splitting the parts, in order to see a summary table*

```{r}

for (i in 1:length(filtered_list)) {
  file <- paste0("C:/Users/smanz/OneDrive/Escritorio/TFM/Results/Exon_COUNTS_noaggegation_specificity/Local_Events/Filtered_Events/", filtered_list[i])
  LocalEvents <- read.csv2(file, header = TRUE, sep = ";", row.names = NULL)
  
  colnames(LocalEvents) <- c("gene_name", "dPSI", "p.value")
  
  # Split gene_name by ":"
  gene_name_split <- strsplit(as.character(LocalEvents$gene_name), ":")
  genelocalevent <- sapply(gene_name_split, `[`, 1)
  
  # Split the results by ";"
  split_vector <- strsplit(genelocalevent, ";")
  gene_name <- sapply(split_vector, `[`, 1)
  local_event <- sapply(split_vector, `[`, 2)
  
  # Create the new data frame
  LocalEvents <- data.frame(gene_name = gene_name, local_event = local_event, dPSI = LocalEvents$dPSI, p.value = LocalEvents$p.value)
  
  # Filter genes matching the pattern
  pattern_matched <- grep(pattern, LocalEvents$gene_name)
  LocalEvents_filtered <- LocalEvents[pattern_matched, ]
  
  # Remove duplicates
  LocalEvents_distinct <- distinct(LocalEvents_filtered)
  
  # Create a dynamic name for the object
  object_name <- paste0("InterestGenes_DF_P", 53 + i - 1)
  
  # Assign the final dataframe to an object with a dynamic name
  assign(object_name, LocalEvents_distinct)
}


```

## Merged and edited data frame

```{r}

Edited_DF <- rbind(InterestGenes_DF_P53, InterestGenes_DF_P54, InterestGenes_DF_P56, InterestGenes_DF_P63, InterestGenes_DF_P67, InterestGenes_DF_P76, InterestGenes_DF_P77, InterestGenes_DF_P79, InterestGenes_DF_P80, InterestGenes_DF_P83, InterestGenes_DF_P84, InterestGenes_DF_P85, InterestGenes_DF_P91, InterestGenes_DF_P93, InterestGenes_DF_P96, InterestGenes_DF_P98)


Edited_DF$patient <- c("Patient 53", "Patient 54", "Patient 56", "Patient 63", "Patient 67", rep("Patient 76", 4), rep("Patient 77", 3), rep("Patient 79", 2), "Patient 80", "Patient 83", "Patient 84", rep("Patient 85", 2), "Patient 91", "Patient 93", "Patient 96", rep("Patient 98", 2))

Edited_DF <- arrange(Edited_DF, Edited_DF$gene_name)

Edited_DF$gene_names <- c(rep("CDH1",2), rep("MLH1",7), rep("PALB2",2), rep("RAD51D",2), rep("RAD51C",2), rep("TP53",4), rep("ATM",3), rep("PTEN",2))
  

Final_DF_LocalEvents <- data.frame(Patient = Edited_DF$patient, Gene_Name = Edited_DF$gene_names, rest = Edited_DF)

colnames(Final_DF_LocalEvents) <- c("Patient", "Gene name", "Gene ID", "Local Event", "dPSI", "p.value")

Final_DF_LocalEvents <- Final_DF_LocalEvents[,1:6]


#write.table(Final_DF_LocalEvents, "Final_DF_LocalEvents.tsv", quote = F, row.names = F, col.names = T, sep = "\t")

```


# Session info


```{r}

sessionInfo()

```







