---
title: "OUTRIDER OUTlier in RNA-Seq fInDER"
author: "Sergio Manzano"
date: "2024-06-04"
output:
  BiocStyle::html_document:
    theme: spacelab
    number_sections: true
    toc_float: true
    toc_depth: 3
---

The main article of this tool is: https://www.nature.com/articles/s41596-020-00462-5

```{r, echo=FALSE}

setwd("C:/Users/smanz/OneDrive/Escritorio/TFM/Results/DROP_analysis")

```


# **OUTRIDER**

## *OUTRIDER first analysis*

This package is coming from: https://github.com/gagneurlab/OUTRIDER

### Library loading

```{r, warning=FALSE, message=FALSE}

# First analysis
library(OUTRIDER)
library(DT)
library(ggplot2)
library(plotly)

```

### Load the *gene counts (tsv)* obtained from the RNA-seq pipeline (nf-core) and put in the correct format (rownames modified)

```{r}

gene_counts <- read.csv("C:/Users/smanz/OneDrive/Escritorio/TFM/Results/DROP_analysis/salmon.merged.gene_counts.tsv", sep = "\t")
rownames(gene_counts) <- gene_counts$gene_id
gene_counts <- gene_counts[,3:55]

```

### Create an OutriderDataSet from the counts table

```{r}

int_gene_counts <- as.data.frame(lapply(gene_counts, as.integer)) # We need to convert all the count values to integer numbers
rownames(int_gene_counts) <- row.names(gene_counts) # Reset the row names

Outrider_DS <- OutriderDataSet(countData=int_gene_counts) # Create the outrider data set

```

### Filter out non expressed genes

```{r}

Outrider_filtered <- filterExpression(Outrider_DS, minCounts=TRUE, filterGenes=TRUE)

```

### Run full OUTRIDER pipeline (control, fit model, calculate P-values)

```{r, warning=FALSE, message=FALSE}

Outrider_results <- OUTRIDER(Outrider_filtered)

```
### Results (only significant)

The following table contains those RNA outliers that have a **p.adjust < 0.05**. The p-value has been obtained *automatically following the workflow defined by the authors*, but it has not been calculated manually.

In this table we have all the genes, not only the genes of interest (but they are also included).

```{r}

res_significant <- results(Outrider_results) 

datatable(res_significant, 
          options = list(paging = TRUE, pageLength = 10, searching = TRUE, ordering = TRUE, info = TRUE))

```

#### Check if there is any gene of interest in the obtained results

**We can see that any of the genes of interest is present**

```{r}

genes <- c("BRCA1", "CDH1", "MLH1", "PALB2", "MSH2", "RAD51C", "MSH6", 
           "BRIP1", "BARD1", "BRCA2", "TP53", "ATM", "PTEN", "CHEK2", "RAD51D")


res_significant[res_significant$geneID %in% genes]

```


### Results for the genes of interest without taking into account the p.adj (padjCutoff = 1)

The following table contains all the RNA outliers, without taking into account the p.Value or p.adj. This is an intermediate step to continue with the analysis.

```{r}

# Genes of interest
genes <- c("BRCA1", "CDH1", "MLH1", "PALB2", "MSH2", "RAD51C", "MSH6", "BRIP1", "BARD1", "BRCA2", "TP53", "ATM", "PTEN", "CHEK2", "RAD51D")

# Display all the results
res <- results(Outrider_results, padjCutoff = 1) 

# Make the selection
res_selection <- res[res$geneID %in% genes]

# Display the results of the genes of interest 
datatable(res_selection, 
          options = list(paging = TRUE, pageLength = 10, searching = TRUE, ordering = TRUE, info = TRUE))


```


#### Results for the genes of interest calculating the p.adj manually

The following table lists RNA outliers, along with the manually calculated p.adjust values (*p.adjust function*). This represents an intermediate step in the ongoing analysis.

In this table we have only the genes of interest.

```{r}

# Calculate the p.adjusted manually (only taking into account the subset of values)
manually_p <- p.adjust(res_selection$pValue, method = "fdr", n = length(res_selection$pValue))

# Substitute the previous padj by the manually calculated padj
res_selection$padjust <- manually_p

# Display the results of the genes of interest with the p.values adjusted manually
datatable(res_selection, 
          options = list(paging = TRUE, pageLength = 10, searching = TRUE, ordering = TRUE, info = TRUE))


```

### Table and Dot-plot of the genes that have a padjust value < 0.05

The following table shows those genes that meet the condition of having a p.adjust < 0.05

```{r}

# Make the selection
subset <- res_selection[res_selection$padjust < 0.05, ]

# Create the table

datatable(subset, 
          options = list(paging = TRUE, pageLength = 10, searching = TRUE, ordering = TRUE, info = TRUE))

```

Table to include in the manuscript

```{r}

datatable(subset[, c("geneID", "sampleID", "padjust", "normcounts")], 
          options = list(paging = TRUE, pageLength = 10, searching = TRUE, ordering = TRUE, info = TRUE))


```

Below is the plot of normalized readings across the samples. The genes shown in the previous table are colored.

```{r Normcounts plot, fig.align='center'}

# Create the graphic
dotplot <- ggplot(res_selection, aes(x = sampleID, y = normcounts, color = padjust < 0.05)) +
  geom_point(size = 2) +
  
  scale_color_manual(values = c("grey50", "red"), guide = FALSE) +
  geom_text(aes(label = ifelse(padjust < 0.05, as.character(geneID), "")),
            color = ifelse(res_selection$padjust < 0.05, "blue", "black"),
            vjust = -0.5, size = 3) +
  
  labs(x = "Samples", y = "Norm Counts", title = "Normalized Counts by Samples") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) 


# Create an interactive graph
dotplot_interactive <- ggplotly(dotplot)
dotplot_interactive

```
